strucplots---Visualizing higher-dimensional Contingency Tables in \pkg{vcd}

### 2005-08-01 trunk/vcd/inst/doc/strucplot.Rnw
Now really fixed the conditioning formula in mosaic.formula.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@417 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{center}
<<Conditioning,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
mosaic(~ Class + Age | Sex, data = Titanic, split = TRUE)
@
\caption{Mosaic plot for the Titanic data (expected values).}
\label{fig:conditioning}
\end{center}
\end{figure}

\noindent Note, however, that the plots in the ``pseudo-strata'' are
distorted since they are not corrected for the marginal
distribution(s) of the conditioning variables. Indeed,
the \code{cotabplot()} function would do a much better job here (see
next section).

>>>>

\begin{center}
<<Conditioning,fig=TRUE,echo=FALSE,height=6,width=7,results=hide>>=
mosaic(~ Class + Age | Sex, data = Titanic, split = TRUE)
@
\caption{Mosaic plot for conditional independence structures.}
\label{fig:conditioning}
\end{center}
\end{figure}

\noindent The effect of using this kind of formula is that
conditioning variables are permuted before the conditioned variables
in the table, and that \code{spacing\_conditional()} is used to better
distinguish conditioning from conditioned dimensions.
Note, however, that the plots in the ``pseudo-strata'' are
distorted since they are not corrected for the marginal
distribution(s) of the conditioning variables. Indeed,
the \code{cotabplot()} function would do a much better job here (see
next section).
